You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-26 paper/paper.tex
merged changes

We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
dictionary entries are presented in table \ref{dictionary_example}.

@@

>>>>

We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
dictionary entries are presented in table \ref{dictionary_example}. As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.

For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ... I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit":

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|l|}
    \hline
    conditional probability & target & source \\
    \hline
    \hline
    0.0000790755 & PERCHANCE & maybe \\
    \hline
    0.00003691883 & PERADVENTURE & maybe \\
    \hline
    0.00007524298 & HAPLY & maybe \\
    \hline
    0.00007141065 & HAPPILY & maybe \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Word frequency in target language}
  \label{word_frequency}
\end{table}
